MNRAS \LaTeXe\ template -- title goes here

### 2018-08-23 paper.tex
Adding detailed bullet points for the introduction.  Added acknowledgments.

\li Here are some relevant papers that studied the minimum halo mass
with simulations or ones that developed an analytical model of the
halo mass.  We will probably cite most of these in the introduction.

@@

@@

We used Enzo \citep{Enzo}.

@@

@@

@@

>>>>

\noindent Here are some relevant papers that studied the minimum halo
mass with simulations or ones that developed an analytical model of
the halo mass.  We will probably cite most of these in the
introduction.

@@

\medskip
\noindent Here are some bullet points to guide the intro's narrative.

\li The first generation of stars transformed a cold and dark universe
by illuminating and enriching up their neighborhoods with radiation
and heavy elements.

\li They are metal-free (Population III; Pop III) and are thought to
be generally massive and thus a substantial fraction will generate
prodigious amounts of ionizing photons and will end their lives in
supernovae \citep[e.g.][]{Schaerer02, Heger02}.

\li Once a halo becomes chemically enriched, by definition, it cannot
form Pop III stars anymore, marking the end of metal-free star
formation in that pregalactic object.  Numerical studies have shown
that turbulence within halos can mix metals well down to their
resolution limit \citep[][and more]{Wise08_Gal, Greif10}.

\li Given the paradigm of hierarchical structure formation, halos grow
through smooth accretion and successive mergers of smaller halos.  But
in which halos do these first generations of stars form?  Their
formation rates and locations are important to constrain because they
influence the very beginnings of galaxy formation and cosmic
reionization.

\li Without metals and dust to facilitate efficient radiative cooling,
Pop III stars rely on \hh{} formation to cool the gas.  These
molecules are however fragile to dissociation from Lyman-Werner
(LW) radiation in the energy range 11.2--13.6~eV.

\li Diffuse gas is optically thin to LW radiation, thus a background
builds over time and can suppress \hh{} formation and thus Pop III
star formation.  Furthermore, nearby sources of LW radiation can
dissociate \hh{} in minihalos.

\li Other sources of the suppression of Pop III star formation are
streaming baryonic velocities, arising from recombination, and
dynamical heating, occuring during the virialization of halos.

\li Previous work have mainly investigated and established the lower
limit for a halo to host Pop III stars.  However, subsequent
simulations have shown that they don't necessarily form at this
minimum, whereas other physical processes (mentioned above) play a
role.

\li In this paper, we focus on the distribution of host halo masses,
not just the minimum, and its dependence on redshift and the LW
background, augmenting the results from prior work.

\medskip
\noindent Include the ``typical'' overview of the paper's sections
last in the introduction.

@@

We used \enzo{} \citep{Enzo} and \yt{} \citep{yt_full_paper}.

@@

See \citet{Wise14}.

@@

Temporary list of figures:
\begin{enumerate}
\item One
\item Two
\end{enumerate}

@@

JHW is supported by National Science Foundation grants AST-1614333 and
OAC-1835213, NASA grant NNX17AG23G, and Hubble theory grant
HST-AR-14326.  We thank the support staff at Georgia Tech's PACE,
where we ran this simulation.  The freely available plotting library
{\sc matplotlib} \citep{matplotlib} was used to construct numerous
plots within this paper. Computations and analysis described in this
work were performed using the publicly-available \enzo{} and \yt{}
codes, which is the product of a collaborative effort of many
independent scientists from numerous institutions around the world.
